```{r}

install.packages("rgdal")
```
```{r}
install.packages(c("sf", "tmap", "tmaptools", "RSQLite", "tidyverse"), 
                 repos = "https://www.stats.bris.ac.uk/R/")
```
```{r}

```

```{r}
library(sf)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(rgdal)
library(janitor)
# change this to your file path!!!

```
```{r}
boro <- st_read("//ad.ucl.ac.uk/homea/ucfnina/Downloads/dissertation/statistical-gis-boundaries-london/ESRI/London_Borough_Excluding_MHW.shp")

boro_sf <- st_as_sf(boro)
```
```{r}
lsoa <- st_read("//ad.ucl.ac.uk/homea/ucfnina/Downloads/dissertation/statistical-gis-boundaries-london/ESRI/LSOA_2011_London_gen_MHW.shp")%>%
    st_transform(., 27700)

lsoa_sf <- st_as_sf(lsoa)

```{r}

```



```{r}
zoopla <-  read_csv("//ad.ucl.ac.uk/homea/ucfnina/Downloads/dissertation/Zoopla_6_0814.csv")  
```
```{r}
count_cloumns1 <- sapply(zoopla,function(col)length(na.omit(col)))

print(count_cloumns1)
```



```{r}
zoopla_pionts<- zoopla%>%
  st_as_sf(., coords = c("lon", "lat"), 
                   crs = 4326) %>%
    st_transform(., 27700)
```
```{r}
zoopla_join <-st_join(zoopla_pionts,lsoa_sf,join=st_within)

```
```{r}
price<-zoopla_join %>%
  group_by(LAD11NM)%>%
  summarise(boro_price=mean(price_last,na.rm=TRUE),
            pre_price = mean(ifelse(pre == 1,price_last,NA),na.rm=TRUE),
            during_price = mean(ifelse(during == 1,price_last,NA),na.rm=TRUE),
            post_price = mean(ifelse(post == 1,price_last,NA),na.rm=TRUE),
            post1_price = mean(ifelse(post1 == 1,price_last,NA),na.rm=TRUE),
            post2_price = mean(ifelse(post2 == 1,price_last,NA),na.rm=TRUE),
            )
```

```{r}
price_lsoa<-zoopla_join %>%
  group_by(LSOA11NM)%>%
  summarise(lsoa_price=mean(price_last,na.rm=TRUE),
            pre_price = mean(ifelse(pre == 1,price_last,NA),na.rm=TRUE),
            during_price = mean(ifelse(during == 1,price_last,NA),na.rm=TRUE),
            post_price = mean(ifelse(post == 1,price_last,NA),na.rm=TRUE),
            post1_price = mean(ifelse(post1 == 1,price_last,NA),na.rm=TRUE),
            post2_price = mean(ifelse(post2 == 1,price_last,NA),na.rm=TRUE),
            )
```

```{r}
price <- price %>%
  mutate(
    diff_pre_during = ((during_price - pre_price)/pre_price)*100,
    diff_during_post = ((post_price - during_price)/during_price)*100,
    diff_during_post1 = ((post1_price - during_price)/during_price)*100,
    diff_post1_post2 = ((post2_price - post1_price)/post1_price)*100
  )
```

```{r}
price_lsoa <- price_lsoa %>%
  mutate(
    diff_pre_during = ((during_price - pre_price)/pre_price)*100,
    diff_during_post = ((post_price - during_price)/during_price)*100,
    diff_during_post1 = ((post1_price - during_price)/during_price)*100,
    diff_post1_post2 = ((post2_price - post1_price)/post1_price)*100
  )
```

```{r}
price <- st_drop_geometry(price)
price_lsoa <- st_drop_geometry(price_lsoa)
```

```{r}
count_cloumns2 <- sapply(zoopla_pionts,function(col)length(na.omit(col)))

print(count_cloumns2)
```

```{r}

```




```{r}
boro_price_plot <- boro_sf %>%
  merge(.,
        price,
        by.x="NAME", 
        by.y="LAD11NM")
```


```{r}
library(tmap)
tmap_mode("plot")
# change the fill to your column name if different
diff_pre_during <- tm_shape(boro_price_plot) +
  tm_borders() +
  tm_fill(c("diff_pre_during", "diff_during_post", "diff_during_post1", "diff_post1_post2"), 
          title = "Legend Title")


```


```{r}
write.csv(price, "//ad.ucl.ac.uk/homea/ucfnina/Downloads/dissertation/boro_price.csv")
write.csv(price_lsoa, "//ad.ucl.ac.uk/homea/ucfnina/Downloads/dissertation/lsoa_price.csv")
```
```{r}
zoopla_join2 <- st_drop_geometry(zoopla_join)

write.csv(zoopla_join2, "//ad.ucl.ac.uk/homea/ucfnina/Downloads/dissertation/zoopla_join0822.csv", row.names = FALSE)
```


